\part{Resources}
\chapter{Brands}\label{Brands}
One of the major plot-hooks of the campaign centers around the divine brands. There are two ways a character can acquire a brand; they can take the Branded One background, or they can complete a special trial set by the god associated with the brand. Every person of one of the lineages created by the gods is eligible to have a patron god and take the Branded One background. Usually, a character's patron god is the same god as the one that created their lineage. There are exceptions to this, and it often makes for good roleplaying to explore why a god might have chosen one of your adventurers. The brands earned in trials can be acquired by any lineage, including those who are planar travelers and not one of the 16 lineages created by the gods of the plane.
\section{Branded One Background}\label{Branded One}
If your campaign intends to follow the main plothooks laid out in this guide, and your players are of a lineage created by the gods, they should take the Branded One background. This background grants them access to a brand which grants elemental magic associated with their patron god. As the Dungeon Master, you can choose to assign your player a patron god that fits with their backstory, or roll a d100 for each player taking the Branded One background and determine their god from the table below.
\begin{DndTable}[header=Brands,width=0.5\textwidth]{XX} 
Dice Roll & God \\
1-49 & The creator god of the character's lineage \\
50-59 & Shin \\
60-62 & Amalthea \\
63-65 & Daled \\
66-68 & Harpalyke \\
69-71 & Iona \\
72-74 & Khof \\
75-77 & Merope \\
78-80 & Praxidike \\
81-83 & Pasiphae \\
84-86 & Sinope \\
87-89 & Taygeta \\
90-92 & Themisto \\
93-95 & Tsadek \\
96 & Lysithea \\
97 & Meneas \\
98 & Taranis \\
99 & Tes \\
100 & Yarfinn \\
\end{DndTable}
Some gods are more common than others. Five gods in particular are much rarer than the others. Lysithea is very particular about only caring for orcs, her creation. Being selected by Lysithea as a non-orc character might mean she believes the character will be a great ally to the orcs.\\
Meneas's lineage, the Lurkers, are nearly extinct, and he spends his time trying to thwart the Restorationist Gods (see Chapter~). Being selected by Meneas might be he has a special mission or message to warn the character of the Restorationist Gods.\\
Taranis never created a race successfully, and cares little for mortals. Being selected by Taranis might mean he plans to use the character to bring about the restoration of the aberroth.\\
Tes has chosen to make her duty the re-purposing of the Immylium (or souls) of corpses and bringing them to new bodies. A character chosen by Tes might be selected with a purpose to destroy a person or force that is preventing Immylium from returning to the natural cycle of reincarnation.\\
Yarfinn, along with Taranis is the other restorationist god. He might choose a character if they believe the character can contribute to a world he believes rightfully belongs to the aberroth.\\
On the other hand, Shin is much more likely than other gods to patronize the other lineages. Shin created humans, but tries to avoid playing favorites.\\
\subsection{Branded One Features}
A character with the Branded One background has been marked by a Great Brander, a powerful shaman who can determine a person's patron god. When a character receives this mark, it appears in the form of a brand on their wrist, and grants them access to spells as their character levels up. At 1st level, the brand grants access to a cantrip, as shown in the table at the end of the chapter. At higher levels, the brand grants access to spells at the levels shown in the table. Each of these spells can be cast once, with no material components or focus needed, as long as the hand with the branded wrist is empty. You use your constitution as your spellcasting modifier for spells cast in this way. You regain the use of these spells after completing a long rest.
\newgeometry{left=0.2in,right=0.2in}
\begin{DndTable}[header=Brands,width=\textwidth]{XXXXXXXXXXXX} 

        \textbf{God} & \textbf{Lineage} & \textbf{Element} & \textbf{Level 1} & \textbf{Level 5} & \textbf{Level 9} & \textbf{Level 13} & \textbf{Level 17} &\textbf{Level 20}\\ \hline
        Amalthea & Elves & Illusion & Minor Illusion & Silent Image & Mirror Image & Fear & Hallucinatory Terrain & Mislead \\ 
        Daled & Crystallin & Ice & Frostbite & Frost Fingers & Snillloc’s Snowball Storm & Sleet Storm & Ice Storm & Cone of Cold \\ 
        Harpalyke & Aarakocra & Air & Gust & Feather Fall & Warding Wind & Fly & Summon (Air) Elemental & Freedom Of The Winds \\ 
        Iona & Flameblooded & Fire & Create Bonfire & Burning Hands & Aganazzer’s Scorcher & Ashardalon’s Stride & Fire Shield & Immolation \\
        Khof & Goblins & Alchemy and Infusion & Prestidigitation & Absorb Elements & Jim’s Glowing Coin & Remove Curse & Fabricate & Hallow \\ 
        Lysithea & Tieflings & Emotion & Friends & Cause Fear & Enthrall & Antagonize & Charm Monster & Dream \\ 
        Meneas & Lurkers & Shadows & Control Shadows* & Fog Cloud & Darkness & Hunger of Hadar & Shadow of Moil & Danse Macabre \\ 
        Merope & Arboreans & Plants & Thorn Whip & Entangle & Wither and Bloom & Plant Growth & Grasping Vine & Wrath of Nature \\ 
        Praxidike & Kobolds & Lightning & Lightning Lure & Thunderwave & Shatter & Lightning Bolt & Storm Sphere & Bolt Jump* \\ 
        Pasiphae & Dragonborn & Sound and Language & Thunderclap & Dissonant Whispers & Magic Mouth & Thunderstep & Choir of Angels* & Geas \\ 
        Shin & Humans & Health & Spare the Dying & Healing Word & Lesser Restoration & Mass Healing Word & Aura of Purity & Greater Restoration \\ 
        Sinope & Orcs & Combat & Primal Savagery & Zephyr Strike & Enlarge/ Reduce & Haste & Freedom Of Movement & Circle of Power \\ 
        Taranis & None & Light & Light & Chromatic Orb & Moonbeam & Daylight & Color Wheel* & Wall of Light \\ 
        Taygeta & Seafolk & Water & Shape Water & Create or Destroy Water & Lesser Water Walk* & Wall of Water & Watery Sphere & Maelstrom \\ 
        Tes & None & Death and Rebirth & Chill Touch & False Life & Gentle Repose & Summon Undead & Spirit of Death & Raise Dead \\ 
        Themisto & Gnomes & Metal & Sword Burst & Tenser’s Floating Disk & Heat Metal & Galder’s Tower & Leomond’s Secret Chest & Steel Wind Strike \\ 
        Tsadek & Fairies & Creatures & Infestation & Animal Friendship & Flock of Familiars & Conjure Animals & Find Greater Steed & Insect Plague \\ 
        Yarfinn & Dwarves & Stone and Earth & Mold Earth & Earth Tremor & Earthbind & Meld Into Stone & Stoneskin & Transmute Rock \\ 

\end{DndTable}
\small{* Spell mechanics listed in Chapter~\ref{Spells}}
\restoregeometry