\part{Introduction} \label{Intro}
\section{Introduction}
\DndDropCapLine{W}{elcome to Sunday, a continent} packed to the brim with adventure. This book is primarily focuses on a Level~1-20 campaign centered in the Commonwealth of Kiraki, a country unaware of a rising threat and deadset on adhering to self-destructive old ways and troubled traditions. In addition to the main campaign, there are several one-shot settings around the continent, which can serve as extra locations to explore if your party is particularly expeditious in exploring the wider world. This book is developed for the Dungeons and Dragons 5th Edition rule set, has appendices containing all new mechanics, races, class and subclasses, feats, backgrounds, locations, magical items, characters, and monsters to keep a party enchanted and ready for action and exploration. \\

\section{Character Building}
Tailored for a party of four, this adventure can also work for five to six players if the encounters are appropriately adjusted to make them slightly more difficult. This Campaign Book will guide the Dungeon Master to help their players create rich, unique characters that fit into the Commonwealth of Kiraki. \\
The first thing to decide as the Dungeon Master is whether you would like to run the campaign from the very beginning, and follow the overarching narratives of this campaign book closely. If you do, then you should encourage the players to take the new Branded One background, and indicate that the particular brand they receive will not be determined until partway through the first session.\\
If the players would like characters that are very much at home in Kiraki, they should select from the races Arborean, Elf, Dwarf, Human, Gnome, Seafolk, or Goblin. These are the races that are protected under the Compact of the Seven Races, the legal document establishing the Commonwealth of Kiraki. \\
If the player would like a somewhat distinctive appearance in the setting, at the cost of being occasionally judged harshly by the inhabitants of Kiraki, the player may choose from any of the other \textbf{Gods' Chosen races}. There are 18 gods in this setting, and all save two created a race. The other races created by the gods of this realm are Dragonborn, Fairy, Lurker, Flameblooded, Orc, Tiefling, Crystallin, AIRRACE, and LIGHTNINGRACE. Orcs and Tieflings are uniquely hated in Kiraki, and characters without means of disguise will likely suffer significant prejudice or violence. Lurkers are rumored to be extinct, but there do remain a few isolated communities.\\
All of the other official Dungeons and Dragons races are allowed to be played as well, at the Dungeon Masters discretion. These races are only present as planar travelers and are extremely uncommon in the world. One further exception is the Warforged race. In this setting, Warforged are the creations of Amcysians, humans in the country west of Kiraki. The Amcysians have harvested the souls of murdered beings in the form of Immylium, and infused them into metal creations of war. Warforged are mostly programmed to be loyal to Amcys, though a player character Warforged could be created with a backstory where their programming went wrong, or there was an infiltration of the factory where Warforged were developed.
\subsection{The Branded One Background}

\section{The Overarching Narratives}
\section{The Cosmology and Gods}

