\chapter{Spells}\label{Spells}

\subsection{Bolt Jump}
\textit{5th Level conjuration}
\hfill \break
\paragraph{Casting Time} 1 action
\paragraph{Range} Self
\paragraph{Components} V, S, M (A pinch of scorched earth)
\paragraph{Duration} Up to 10 minutes\\
\hfill \break
You change into a bolt of lightning and leap into the sky. For the duration, you can travel in a straight line in one direction, up to a total distance of 20 miles if you use the whole 10 minutes. When you have reached the end of your leap, you slam to the ground. \\
You have no senses during the travel, and cannot pick your exact landing spot, only an approximate location. All creatures within 5 feet of your landing point, including yourself, must make a dexterity saving throw, on a failure taking 3d10 lightning damage.
\hfill \break
\paragraph{Spell Lists} Artificer, Cleric, Druid, Paladin, Ranger

\subsection{Choir of Angels}
\textit{4th-level evocation}
\hfill \break
\paragraph{Casting Time} 1 action
\paragraph{Range} 60 feet
\paragraph{Components} V
\paragraph{Duration} Instantaneous\\
\hfill \break
You summon a heavenly chorus of voices to an area defined by a circle of radius 20 feet within range. All creatures in the circle with evil alignments must make a charisma saving throw, taking 8d8 psychic damage on a failed save. 
\hfill \break
\paragraph{At Higher Levels} When you cast this spell using a spell slot of 5th level or higher, the target takes an additional 2d8 of damage for each level above 4th.
\hfill \break
\paragraph{Spell Lists} Cleric, Paladin, Wizard

\subsection{Color Wheel}
\textit{4th-level evocation}
\hfill \break
\paragraph{Casting Time} 1 action
\paragraph{Range} 60 feet
\paragraph{Components} V, S, M (bristles from a paintbrush)
\paragraph{Duration} Concentration, up to 1 minute\\
\hfill \break
Choose a target that you can see within range. A wheel of color surrounds the target. Roll a d6 to determine the starting Active Color. Refer to the color wheel chart to identify the Active Color.
\\
While under the effects of the color wheel, the target must make a saving throw at the start of each turn corresponding to the Active Color. On a failed save, the target takes 3d12 damage of the damage type associated with the Active Color. On a successful save, the target takes half as much damage.
\\
You can use a bonus action on each of your subsequent turns to advance the Active Color on the chart by one spot. The color progression is cyclic and continues until the spell ends or the starting color is reached again.
\\
Note that the target can only take damage from each color once while the spell is in effect. \\
\begin{DndTable}[header=Color Wheel Chart, width=0.45\textwidth]{XXXX}
    \textbf{Dice Roll}  & \textbf{Active Color} & \textbf{Damage Type} & \textbf{Saving Throw}\\
    1 & Red & Fire & Dexterity\\
    2 & Orange & Necrotic & Charisma\\
    3 & Yellow & Lightning & Intelligence\\
    4 & Green & Poison & Constitution\\
    5 & Blue & Cold & Strength \\
    6 & Purple & Psychic & Wisdom
\end{DndTable}  
\hfill \break
\paragraph{At Higher Levels} When you cast this spell using a spell slot of 5th level or higher, the target takes an additional d12 of damage for each level above 4th.
\hfill \break
\paragraph{Spell Lists} Artificer, Bard, Druid


\subsection{Gather Shadows}
\textit{Evocation cantrip}
\hfill \break
\paragraph{Casting Time} 1 action
\paragraph{Range} Self
\paragraph{Components} S
\paragraph{Duration} Concentration, up to 1 minute\\
\hfill \break
You gather shadows around yourself, making you hard to see. You have advantage on stealth checks, and enemies without darkvision have disadvantage on attack rolls against you for the duration of the spell. The shadows do not count as magical darkness.
\hfill \break
\paragraph{Spell Lists} Bard, Sorcerer, Warlock


\subsection{Lesser Water Walk}
\textit{2nd-level transmutation (ritual)}
\hfill \break
\paragraph{Casting Time} 1 action
\paragraph{Range} Self
\paragraph{Components} V, S, M (a seagull feather)
\paragraph{Duration} Up to 1 hour\\
\hfill \break
This spell grants the ability to move across any liquid surface – such as water, acid, mud, snow, quicksand, or lava – as if it were harmless solid ground (creatures crossing molten lava can still take damage from the heat). This only applies to yourself.

If you are submerged in a liquid, the spell carries you to the surface of the liquid at a rate of 60 feet per round.
\hfill \break
\paragraph{Spell Lists} Artificer, Cleric, Druid, Ranger, Sorcerer